R Markdown Features

### 2018-07-10 GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.Rmd
up

---
title: "Create Beamer Slide with R Markdown"
subtitle: "A Reproducible Example"
author: "Yongfu, Liao"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
institute: "National Taiwan University"
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: true
    latex_engine: xelatex
    includes:
        in_header: header_beamer.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
date_text <- "format(Sys.Date(), '%B %d, %Y')"
```

@@

## Reproduce This slide: yaml Header (Cont.)
```yaml
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: true
    latex_engine: xelatex
    includes:
        in_header: header_beamer.tex
---
```

> - Links  
[header_beamer.tex](https://github.com/liao961120/local_depend/blob/master/style_sheets/header_beamer.tex)  
[Source Dir](https://github.com/liao961120/local_depend/tree/master/GitHubPage/my_R_book/Rmarkdown_features/beamer)

@@

\column{0.25\textwidth}
Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text.
\end{columns}

@@

```tex
\begin{columns}
\column{0.75\textwidth}
```
    `r ''````{r out.width="75%"}
    library(ggplot2)
    ggplot(iris, aes(x = Sepal.Width,
                     y = Sepal.Length)) +
        geom_point(aes(color = Species),
                   show.legend = F)
    ```
```tex
\column{0.25\textwidth}
Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text.
\end{columns}
```

@@

Remember to set `incremental: true` in the yaml header if you want this feature.

1. Item 1

2. Item 2

3. Item 3

>>>>

---
title: "Create Beamer Slide with R Markdown"
subtitle: "A Reproducible Example"
author: "Yongfu, Liao"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
institute: "National Taiwan University"
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: false
    latex_engine: xelatex
    includes:
        in_header: header_beamer.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
date_text <- "`r format(Sys.Date(), '%B %d, %Y')`"
```

@@

## Reproduce This slide: yaml Header (Cont.)
```yaml
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: false
    latex_engine: xelatex
    includes:
        in_header: header_beamer.tex
---
```

- Links
    - [header_beamer.tex](https://github.com/liao961120/local_depend/blob/master/style_sheets/header_beamer.tex)
    - [Source Directory](https://github.com/liao961120/local_depend/tree/master/GitHubPage/my_R_book/Rmarkdown_features/beamer) of this Presentation
    - [More](https://liao961120.github.io/notes/rmd_features.html) about R Markdown

@@

\column{0.25\textwidth}
R is a collaborative project with many contributors.
Type `contributors()` for more information and
`citation()` on how to cite R or R packages in publications.
\end{columns}

@@

```tex
\begin{columns}
\column{0.75\textwidth}
```
    `r ''````{r out.width="75%"}
    library(ggplot2)
    ggplot(iris, aes(x = Sepal.Width,
                     y = Sepal.Length)) +
        geom_point(aes(color = Species),
                   show.legend = F)
    ```
```tex
\column{0.25\textwidth}
R is a collaborative project with many contributors.
Type `contributors()` for more information and
`citation()` on how to cite R or R packages in publications.
\end{columns}
```

@@

> 1. Item 1

> 2. Item 2

> 3. Item 3

## Contact

```{r out.width="10%"}
knitr::include_graphics("tux.png")
```

\

Where You can find me:

- [GitHub](https://github.com/liao961120)

- [Personal Page](https://liao961120.github.io/)

### 2018-07-10 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

---
title: "Rmarkdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
str_date <- "`r Sys.Date()`"
```

@@

# Shaped Images {.tabset}

@@

>>>>

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
str_date <- "`r format(Sys.Date(), '%B %d, %Y')`"
```

@@

# Shaped Images (HTML) {.tabset}

@@

# Beamer Slide (PDF)

<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width="550" height="500" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:5px; max-width: 100%;" allowfullscreen></iframe>

[Download](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
